Error Summary (teaching-v1.0)

### 2020-11-24 script/R/preprocessor/filtered/error_summary.Rmd
change paths
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# function
source("./function.R")

# read a text file for ideal performance
dt_ideal <- read.table("./ideal.txt")
colnames(dt_ideal) <- "Pitch"
dt_ideal$RowNr <- 1:nrow(dt_ideal)
setcolorder(dt_ideal, c(2, 1))
# 
dt_onset <- fread(file = "./dt_correct_onset.txt", sep = ",")
dt_offset <- fread(file = "./dt_correct_offset.txt", sep = ",")
error_onset <- fread(file = "./error_onset.txt", sep = ",")
error_offset <- fread(file = "./error_offset.txt", sep = ",")
```

>>>>

# function
source("../function.R")

# read a text file for ideal performance
dt_ideal <- read.table("../ideal.txt")
colnames(dt_ideal) <- "Pitch"
dt_ideal$RowNr <- 1:nrow(dt_ideal)
setcolorder(dt_ideal, c(2, 1))
# 
dt_onset <- fread(file = "./dt_correct_onset.txt", sep = ",")
dt_offset <- fread(file = "./dt_correct_offset.txt", sep = ",")
error_onset <- fread(file = "./error_onset.txt", sep = ",")
error_offset <- fread(file = "./error_offset.txt", sep = ",")
```
